Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-29 review_article.Rmd
begin adding captions to figure 2

```{r choropleth-grid-create, message=FALSE}
library(grid)
library(png)
library(gridExtra)

@@

choropleth_grid <- gridExtra::grid.arrange(grid::rasterGrob(plot1),
                  grid::rasterGrob(plot2), 
                  grid::rasterGrob(plot3),                
                  grid::rasterGrob(plot4), 
                  grid::rasterGrob(plot5), 
                  grid::rasterGrob(plot6),
                  grid::rasterGrob(plot7), 
                  grid::rasterGrob(plot8), 
                  grid::rasterGrob(plot9), ncol=3)

>>>>

```{r choropleth-grid-create, message=FALSE, fig.cap = "Public facing choropleth cancer maps. [Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx), "}
library(grid)
library(png)
library(gridExtra)

@@

choropleth_grid <- gridExtra::grid.arrange(
                  grid::rasterGrob(plot1),
                  grid::rasterGrob(plot2), 
                  grid::rasterGrob(plot3),                
                  grid::rasterGrob(plot4), 
                  grid::rasterGrob(plot5), 
                  grid::rasterGrob(plot6),
                  grid::rasterGrob(plot7), 
                  grid::rasterGrob(plot8), 
                  grid::rasterGrob(plot9), ncol=3)
